Hypertension and microbiome

### 2019-05-27 articletwo.Rmd
Fixing maaslin

```{r maaslin runs, results = 'hide'} 
if (!file.exists("rds/maaslin.rds")) {
    maaslin <- list()
    genus.core.bacteria <- pseq.genus.core %>%
        abundances %>%
        rownames %>%
        replace.brackets %>%
        mygrep(".Bacteria$", .)

    pseq.species %>% meta %>% pull(DIAB) %>% summary
    pseq.genus.core %>% meta %>% pull(DIAB) %>% as.factor %>% summary

    maaslin$genus <- maaslinwrapper(pseq = pseq.genus.core,
                                    looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE",
                                               "HYPERTENSION"),
                                    forced = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X",
                                               "DIAB", "BL_USE_RX_C03",
                                               "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                                    taxa = paste0(genus.core.bacteria, collapse = ","))
    saveRDS(maaslin, file = "rds/maaslin.rds")
} else {
    maaslin <- readRDS("rds/maaslin.rds")
}
```

>>>>

```{r maaslin runs, results = 'hide'} 
if (!file.exists("rds/maaslin.rds")) {

    maaslin <- list()
    genus.core.bacteria <- pseq.genus.core %>%
        abundances %>%
        rownames %>%
        replace.brackets %>%
        mygrep(".Bacteria$", .)
    maaslin$genus <- maaslinwrapper(pseq = pseq.genus.core,
                                    looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE",
                                               "HYPERTENSION"),
                                    forced = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X",
                                               "DIAB", "BL_USE_RX_C03",
                                               "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                                    taxa = paste0(genus.core.bacteria, collapse = ","))

    saveRDS(maaslin, file = "rds/maaslin.rds")
} else {
    maaslin <- readRDS("rds/maaslin.rds")
}
```
